---
title: "Hypercubes"
author: "Paul M"
date: "12/3/2020"
output: html_document
---

Here you are asked to consider the following situation:

Consider n-dimensional unit ‘cubes’:

* n=1 -> line. Coordinates= (x1) [or (x)].
* n=2 -> a square. Coordinates= (x1,x2) [or (x,y)]. 
* n=3 -> a cube. Coordinates= (x1,x2,x3) [or (x,y,z)]. 
* n=4 -> 4-dimensional hypercube. Coordinates= (x1,x2,x3,x4). 
* n=5 -> 5-dimensional hypercube. Coordinates= (x1,x2,x3,x4,x5). 
* n=N -> N-dimensional hypercube. Coordinates= (x1,x2,x3,x4,…,xN).

Let’s suppose that all are unit cubes, so 0 ≤ xi ≤ 1, for all i.

You are asked to address the following questions:

#### Question 1: 
If we sample a point uniformly at random from inside a hypercube, what is the probability that the point is within a distance of 0.1 of the surface?

#### Question 2: 
How can you use your answer to question 1 to find the what proportion of the volume of an n-dimensional hypercube that is within a distance of 0.1 of the surface?

---

Pseudocode for this problem can be found below.


First, set-up some global variables:
```{r}
set.seed(324)  # set the seed for the random number generator to any number you like
NumberOfTrials<-500   # How many trials we will perform
TotalCountNearSurface<-numeric()    # a vector that records how many were close to the surface for each dimension
MaxNumberOfDimensions<-10  # we will go up to this many dimensions
```


Set up a loop to run through the different dimensions, and then for each dimension simulate the procxess of picking a random point. As you do that, keep track of how many fall close to the edge.

```{r}
HowManyCloseToSurface<-0 # A variable to record how often the point is close to the surface in a given dimension
for (j in 1:MaxNumberOfDimensions) {
  HowManyCloseToSurface<-0   # reset your counter
  for (i in 1:NumberOfTrials) {
    
    # add code to pick a point at random in the cube

    # check whether the point is within 0.1 of the surface (how do you check this?)
    # if it is, increase the value of HowManyCloseToSurface by 1
    
    # record the value of HowManyCloseToSurface, this will be your estimate of the prob. of being close to surface
    # store it in a vector (say), so that you can keep track of the number you got for each dimension
  }  
  
  # output the proportion of the volume of the cube that is within 0.1 of the surface
  
}
```

Now plot your estimates of the proportion of the volume that is within 0.1 of the surface (on the y axis)
against the number of dimensions the hypercube has (on the x-axis) and answer thew earlier questions.

##### Extra question. What do you notice about this proportion as N increases? What value do you think it takes for very large N?
